Sulfur Dioxide on Water's Surface

### 2011-04-07 Background.tex
New image for showing system density and surface-location drift

Figure \ref{fig:density-flaw} demonstrates the problem of surface location drift during a simulation. This figure shows the density profile of water and \suldiox~over the course of one of the 10 ns trajectories used in this work. The water density profile (dashed line) is produced by averaging the instantaneous density profile at each timestep in the simulation. The water profile was then fit to a $\tanh$ function (black) to extract the position and width parameters of the water surface. The fitted Gibbs dividing surface has a ``90-10'' width of 8.28 $\AA$. A bulge in the gas-phase (left) side of the water profile is indicative of the drift of the water slab over the course of the trajectory. Thus the calculated location and width from the $\tanh$ line fit are not accurate over long trajectories for defining a stationary reference point. All depth locations in our analyses are calculated relative to the surface location at the corresponding timestep of the trajectories.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/density/Density+SurfaceLocation-flawed.png}
		\caption{Density profiles of \wat~(dashed) and \suldiox~(red) from a 10 ns simulation of the neat-water system with a single sulfur dioxide. The \wat~density profile was fit using a hyperbolic tangent function to extract location and width data. The location of the outer \wat~monolayer was calculated, and the corresponding location distribution (blue) is also plotted. Long simulations of liquid slabs result in drift of the slab location, and the consequent broadening of the water density profile if the surface location is not determined repeatedly throughout the simulation.}
		\label{fig:density-flaw}
	\end{center}
\end{figure}

>>>>

Figure \ref{fig:density-flaw} demonstrates the problem of surface location drift during a simulation. This figure shows the density profile of water and \suldiox~over the course of one of the 10 ns trajectories used in this work. The water density profile and location (dashed line) is produced by averaging the instantaneous density profile at each timestep in the simulation. The water profile was then fit to a $\tanh$ function (black) to extract the position and width parameters of the water surface. The fitted Gibbs dividing surface has a ``90-10'' width of 8.28 $\AA$. A bulge in the gas-phase (left) side of the water density profile is indicative of the drift of the water slab over the course of the trajectory. Thus the calculated location and width from the $\tanh$ line fit are not accurate over long trajectories for defining a stationary reference point. All depth locations in our analyses are calculated relative to the surface location (blue) at the corresponding timestep of the trajectories.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/density/density-location.png}
		\caption{(A) Density profiles of \wat~(dashed) and \suldiox~(red) from a 10 ns simulation of the neat-water system with a single sulfur dioxide. The \wat~density profile was fit (black) using a hyperbolic tangent function to extract location and width data for the water surface. (B) The location of the outer \wat~monolayer was calculated for each simulation timestep (blue), and the surface location from the density fitting was also determined (dashed). Long simulations of liquid slabs result in drift of the slab location, and the consequent broadening of the water density profile if the surface location is not determined repeatedly throughout the simulation.}
		\label{fig:density-flaw}
	\end{center}
\end{figure}
